Toward Centrally Programming Distributed Control Planes

### 2016-01-22 paper/compilation.tex
Adding compiled policy figures.

\para{Aggregation-Induced Black Holes}

@@

@@

>>>>

@@

%\begin{figure}[t!]
%\centering
%\includegraphics[width=.9\columnwidth]{figures/config}
%\caption{Abstract BGP configuration.}
%\label{fig:abgp-config}
%\end{figure}

\newcommand{\Router}[1]{ \textbf{Router #1:} }
\newcommand{\REGEX}[1]{ \text{regex}(#1) }
\newcommand{\PEER}{ \text{peer} }
\newcommand{\COMM} {\text{comm}}
\newcommand{\MED} {\text{MED}}

\begin{figure}[t!]
\begin{lstlisting}[frame=single, mathescape=true] 
$\Router{A}$
  Match $\PEER=C, \COMM=(3,2)$
    Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
$\Router{B}$
  Match $\PEER = C, \COMM = (-,2)$
    Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$ 
           $\MED \leftarrow 81, \PEER \leftarrow W$
  Match $\PEER = C, \COMM = (3,2)$
    Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$ 
           $\MED \leftarrow 81, \PEER \leftarrow W$
$\Router{C}$
  Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
    Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
  Match $\PEER = D, \COMM = (2,2)$
    Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
$\Router{D}$
  Match $\REGEX{X + Y}$
    Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
$\Router{E}$
  Match $\REGEX{Z}$
    Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
\end{lstlisting}
\label{fig:config}
\caption{Abstract BGP router configurations.}
\end{figure}

\begin{figure}[t!]
\begin{lstlisting}[frame=single, mathescape=true] 
$\Router{A}$
  Match $\PEER=C$
    Export $\MED \leftarrow 80, \PEER \leftarrow W$
$\Router{B}$
  Match $\PEER = C$
    Export $\COMM \leftarrow \text{noexport}, \MED \leftarrow 81, \PEER \leftarrow W$
$\Router{C}$
  Match$[LP=99]$ $\PEER = E $
    Export $\PEER \leftarrow B$
  Match $\PEER = D$
    Export $\PEER \leftarrow A,B$
$\Router{D}$
  Match $\REGEX{X + Y}$
    Export $\PEER \leftarrow C$
$\Router{E}$
  Match $\REGEX{Z}$
    Export $\PEER \leftarrow C$
\end{lstlisting}
\label{fig:config-min}
\caption{Abstract BGP minimized configurations}
\end{figure}

@@

\subsection{Aggregation-Induced Black Holes}

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/aggregation}
\caption{Aggregation Safety.}
\label{fig:aggregation-safety}
\end{figure}

For example, imagine we use the earlier data center example from Section~\ref{sec:motivation}, with the policy: $p_{g1} \mapsto end(A)$, where $p_{g1}$ falls under the $p_{g^*}$ aggregate. The data center topology and a simplification of the corresponding product graph are shown in Figure~\ref{fig:aggregation-safety}. Since the compiler knows an aggregate will be placed at $X$, and it knows that for prefix $p_{g1}$, the route will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$ in the product graph. In this case, we could remove the $A$ -- $D$ -- $X$ path first. We would then need to remove any other $A$ -- $D$ or $D$ -- $X$ links from the product graph, although in this case there are none. Next, we could remove the links along the $A$ -- $C$ -- $X$ path, repeating the process. Afterwards, $A$ is disconnected from $X$, so the compiler knowns that 2 is a lower bound from aggregation safety for prefix $p_{g1}$. This process is then repeated for other aggregation locations, in this case router $Y$.

### 2016-01-22 paper/expressiveness.tex
Adding compiled policy figures.

\para{Expressiveness}

>>>>

\section{Expressiveness}

In this section we investigate correctness and expressiveness properties of \sysname. We are mainly concerned with the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures? (2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?

In this section, we compare the expressiveness of the \sysname language to that of BGP.
